---
title: "Amazon_best_selling_books_RMD"
author: "Malay Raj"
date: "2023-05-30"
output:
  word_document: default
  html_document: default
---

## AMAZON BEST SELLING BOOKS FROM 2009 TO 2019 ANALYSIS:

Amazon Top 50 Best Selling Books (made available by Souter Saalu under a CC0 license): Data about Amazon's bestselling
books from 2009 to 2019, categorized into fiction and nonfiction.

## Loading Required Packages.

```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(plyr)
library(skimr)
```


## Displaying my current working directory.

```{r}
getwd()
```


## Collecting the data.

```{r}
Books = read.csv("C:/Amazon top 50 best selling books analysis/bestsellers with categories.csv")
```


## Displaying the first six rows of the dataset.

```{r}
head(Books)
```


## Checking the number of rows and dimension of the dataset.

```{r}
nrow(Books)

dim(Books)
```


## Renaming the column User.Rating to Ratings.

```{r}
Books=plyr::rename(Books, replace=c( "User.Rating" = "Ratings"))
```


## Viewing the new column names.

```{r}
colnames(Books)
```


## Inspecting the dataframe and look for inconguencies.

```{r}
str(Books)
```


## Checking for null values in our dataset.

```{r}
sum(is.null(Books))
```


## Checking for any duplicate values in our dataset.

```{r}
anyDuplicated(Books)
```


## Seeing how many observations fall under each of these columns.

```{r}
table(Books$Genre)
table(Books$Year)
table(Books$Ratings)
```


## CONDUCTNG DESCRIPTIVE ANALYSIS:

Descriptive analysis on few columns.

```{r}
summary(Books$Ratings)
```


```{r}
summary(Books$Reviews)
```


```{r}
summary(Books$Price)
```


Comparing Ratings, Reviews, Price with different Genre.

```{r}
aggregate(Books$Ratings ~ Books$Genre, FUN = mean)
aggregate(Books$Ratings ~ Books$Genre, FUN = median)
aggregate(Books$Ratings ~ Books$Genre, FUN = max)
aggregate(Books$Ratings ~ Books$Genre, FUN = min)
```


```{r}
aggregate(Books$Price ~ Books$Genre, FUN = mean)
aggregate(Books$Price ~ Books$Genre, FUN = median)
aggregate(Books$Price ~ Books$Genre, FUN = max)
aggregate(Books$Price ~ Books$Genre, FUN = min)
```


```{r}
aggregate(Books$Reviews ~ Books$Genre, FUN = mean)
aggregate(Books$Reviews ~ Books$Genre, FUN = median)
aggregate(Books$Reviews ~ Books$Genre, FUN = max)
aggregate(Books$Reviews ~ Books$Genre, FUN = min)
```


## SUMMARY STATISTICS.

```{r}
skimr::skim_without_charts(Books)
```


## DATA VISUALIZATION:

Comparing each genre price values.

```{r}
ggplot(Books) + 
  geom_col(mapping = aes(x=Genre, y=Price, fill=Genre)) + 
  labs(title="Each Genre Price")
```


Comparing each genre price distribution.

```{r}
ggplot(Books, aes(x="", y=Price, fill=Genre)) +
  ggtitle("Each Genre Price Percentage") +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start=0) +
  theme_void() 
```


Checking the number of ratings per year.

```{r}
ggplot(Books) + 
  geom_col(mapping = aes(x=Year, y=Ratings)) +
  labs(title="No of ratings per year")
```


Comparing the rating per genre.

```{r}
ggplot(Books) + 
  geom_col(mapping = aes(x=Genre, y=Ratings)) +
  labs(title="Ratings per genre")
```


Checking number of books sold per genre over 10 years.

```{r}
ggplot(Books, aes(x="", y=Year, fill=Genre)) +
  ggtitle("Books sold per genre over the year") +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start=0) +
  theme_void() 
```


Checking the number of reviews got per year.

```{r}
ggplot(Books) + 
  geom_col(mapping = aes(x=Year, y=Reviews)) +
  labs(title="Reviews per year")
```


Checking the top 5 books over the 10 years period reviews vise.

```{r}
Books %>%
  arrange(-Reviews) %>%
  slice_head(n=10) %>%
  ggplot(aes(reorder(Name, Reviews), Reviews)) +
  geom_point(colour = "blue", size = 3) +
  theme(text=element_text(size=10)) + 
  coord_flip() +
  labs(title = "Top 5 best selling books Review vise", x = "")
```









